---
title: "Southern Rockies Subregion Landscape Assessment"
author: "Team LF"
---

## Goals of this quick demonstration

We will use [LANDFIRE](https://landfire.gov/){target="blank"} products to:

1. Map and summarize past and present ecosystems and ecosystem conditions
2. Explore historical disturbance patterns
3. Summarize patterns of change and management opportunities


The following charts, maps, and graphs are based on current LANDFIRE products, however they are intended only as a starting point for further analysis. 

This introduction will:

* provide context for the past and present ecosystem conditions for each [Southern Rockies Fire Science Network](https://www.southernrockiesfirescience.org/){target="blank"} (SRFSN) "Subregion" (_n=5_)
* demonstrate the power of data visualization to explore ecological patterns and functions using LANDFIRE products
* facilitate an understanding of historical and current conditions on a regional scale

## How to use this web report

* QAQC is ongoing
* Want to share this web app? Simply share the hyperlink
* All maps, input datasets and further assistance can be obtained by contacting the author, [Randy Swaty](mailto:rswaty@tnc.org){target="blank"}


## Assessment Location

The SRFSN Wyoming Sagebrush Subregion is located in Central/South central Wyoming and far northwestern Colorado [Read more](https://www.southernrockiesfirescience.org/wyoming-sagebrush/){target="blank"} 


<br>

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}

library(foreign)
library(sf)
library(terra)
library(tidyverse)
library(raster)


```


```{r read shapefile, message=FALSE, warning=FALSE, include=FALSE}
#  read shape
shp <- st_read("data/") %>% 
  st_transform(crs = 5070) %>%
  st_union() %>%
  st_sf()
```

```{r locator map, message=FALSE, warning=FALSE, echo=FALSE}
library(tmap)

# toggle tmap mode to interactive viewing
tmap_mode("view")

# create a quick interactive map
quickmap <- qtm(shp, borders = "darkgreen",  check.and.fix = TRUE)

quickmap



```


