---
title: "Southern Rockies Subregion Landscape Assessment"
author: "TNC's LANDFIRE Team, Conservation Data Lab"
---

## Goals of this quick demonstration

We will use [LANDFIRE](https://landfire.gov/){target="blank"} products to:

1. Characterize and map past and present ecosystem conditions
2. Explore historical disturbance patterns
3. Summarize patterns of change and management opportunities


The following charts, maps, and graphs are based on current LANDFIRE products, and provide a starting point for further analysis.

This demonstration will:

* provide context for the past and present ecosystem conditions the Southern Rockies Subregion, one of the [Southern Rockies Fire Science Network's](https://www.southernrockiesfirescience.org/){target="blank"} (SRFSN) five Subregions
* demonstrate the power of data visualization to explore ecological patterns and functions using LANDFIRE products
* facilitate an understanding of historical and current conditions on a regional scale

## Assessment Location

The SRFSN Southern Rockies Subregion streches from eastern/southern Wyoming down to northern New Mexico.


<br>

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}

library(foreign)
library(sf)
library(terra)
library(tidyverse)
library(raster)


```


```{r read shapefile, message=FALSE, warning=FALSE, include=FALSE}
#  read shape
shp <- st_read("data/") %>% 
  st_transform(crs = 5070) %>%
  st_union() %>%
  st_sf()
```

```{r locator map, message=FALSE, warning=FALSE, echo=FALSE}
library(tmap)

# toggle tmap mode to interactive viewing
tmap_mode("view")

# create a quick interactive map
quickmap <- qtm(shp, 
                borders = "darkgreen", 
                fill = NULL, 
                check.and.fix = TRUE, 
                basemaps = 'https://server.arcgisonline.com/ArcGIS/rest/services/World_Topo_Map/MapServer/tile/{z}/{y}/{x}',
                title = 'Southern Rockies Subregion',)

quickmap



```

## How to use this web report

* All maps, input datasets and further assistance can be obtained by contacting the author, [Randy Swaty](mailto:rswaty@tnc.org){target="blank"}
* QAQC is ongoing
* To share this web app, simply share the hyperlink




